%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Program Manager} % Job title
{Software Enigneering Course Team Project} % Organization
{Beihang University} % Location
{Oct.2015 - Jan.2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {The first semester in Junior ,I guide the team named \href{http://www.cnblogs.com/buaase}{\textbf{Ruan Jian Gong Cheng}} to develop the team project \href{http://buaaphylab.com/}{\textbf{A Physical Experiment Website}}.}
\item {The site's new registered users increased to nearly nine hundred after two months since launched.And the page views are more than twenty and five thousand. We were the best one both in the alpha and beta stage and I was the 1st in the course all the time as well.}
\item {In the experience of developing this one, I have learned to cohere members of team,to increase cooperation,and to improve enthusiasm of members. The project brought me skills not only on kinds of tools, but also on writing documents and designing architecture.And it turned out to be a successful project.}
\end{cvitems}
}

\cventry
{Developer} % Job title
{AR Program —— Magic Cube} % Organization
{Beihang University} % Location
{Feb. 2014 - May. 2014 } % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {The first semster of freshman, I developed a program named "Magic Cube" with a partner because of the . It is related to augmented reality ,and developed in the base of a repository from Github.}
		\item {It could display some high-quality 3D models,videos and posts by scanning the two-dimension code printed on delivery packing boxes. }
		\item {We use java to develop it(Android APP),and finally it turned out to be a great one so it got 3nd prize in Feng Cup Competiton.I didn't write lots of codes, but I have insisted doing it and learned to do pair programming.}
	\end{cvitems}
}

\end{cventries}