%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Writing}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Leader \& Writer} % Role
{A Guide Book for the Operating System Experiment} % Title
{Git@Oschina} % Location
{Jul. 2015 - Mar. 2016} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {The second semster of sophomore, luckily, I finished overall experiments in operating system, and did well in the final reply,leading to a full mark. The experiment, which was based on MIPS architecture, was transplanted from MIT 6.828. But it had some imperfections such as strange bugs, disordered notes and vague materials.}
\item {Hereupon, I started to write the guide book, in coperation with two friends.We have looked up lots of documents and combined their views with our own experience in the process, finally making a book which was typesetted in Latex, nearly one hundred and forty pages.It was hosted in Git@Oschina. At the same time, we add perfect English notes on every necessary function.	
}
\item {
	As a leader, I made a systematic plan ,in the beginning of writing the guide book. So the progress of writing was carried smoothly. As a writer, I wrote the 2nd,4th,6th chapter and the guide for git in a humorous tone.
}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}